A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-10 survey.tex
A few fixes on the intro paragraph to Section V (this is a tiny commit :))

In order to inject new AI code into the StarCraft game, all recent
tournaments attached to scientific conferences employ the 
Brood War Application Programming Interface 
(BWAPI)\footnote{\url{http://code.google.com/p/bwapi/}} which 
enables replacing the human player interface with a C++ library,
some auxiliary libraries and the bot code. A consequence of this
indirect way of integrating new bots is that every machine can
only run one custom bot, requiring two computers for a 2-player game.

The following subsections summarize the results of all the StarCraft AI competitions held at the AIIDE (Artificial Intelligence for Interactive Digital Entertainment) and CIG (Computational Intelligence in Games) conferences during the past years. Additionally we analyze the statistics from the StarCraft Bot Ladder, where the best bots play against each other all the time.

>>>>

This section reviews the results of the recent international competitions on AI for StarCraft. These competitions, typically co-located with scientific conferences, have been possible thanks to the existence of the the 
Brood War Application Programming Interface 
(BWAPI)\footnote{\url{http://code.google.com/p/bwapi/}}, which 
enables replacing the human player interface with C++ code.
%A consequence of this indirect way of integrating new bots is that every machine can only run one custom bot, requiring two computers for a 2-player game.
The following subsections summarize the results of all the StarCraft AI competitions held at the AIIDE (Artificial Intelligence for Interactive Digital Entertainment) and CIG (Computational Intelligence in Games) conferences during the past years. Additionally we analyze the statistics from the StarCraft Bot Ladder, where the best bots play against each other continuously over time.
